Elephant Seal Age JAE Intraspecific Variation

### 2023-11-09 paper/paperv2.qmd
Getting the doc ready to be a web page

---
title: "Elephant Seal Age JAE Intraspecific Variation"
format: 
  html: 
    echo: false
    fig-width: 4.5
    fig-height: 4.5
    embed-resources: true
    code-fold: true
    code-tools: true
    warning: false
editor: visual
bibliography: references.bib
---

>>>>

---
title: "Elephant Seal Age JAE Intraspecific Variation"
format: 
  html: 
    echo: false
    fig-width: 4.5
    fig-height: 4.5
    code-fold: true
    code-tools: true
    warning: false
editor: visual
bibliography: references.bib
---
